Cover Your Basis: Comprehensive Data-Driven Characterization of the Binary Black Hole Population

### 2022-10-11 src/tex/conclusion.tex
fix href

Non-parametric and data-driven statistical modeling methods have been put to use with great success across the ever-growing field of gravitational 
waves \citep{B_Farr_etal_2014,Littenberg_2015,Mandel_2016,Edwards_2018,Doctor_GPR,Edelman_2021,Vitale_2021,Tiwari_2021_a,Tiwari_2021_b,Edelman_2022ApJ,Tiwari_2022ApJ}. 
We presented a case study exploring how basis splines make for an especially powerful and efficient data driven method of characterizing the binary black hole population observed 
with gravitational waves, along with the associated open source software \textsc{GWInferno} (\href[]{https://git.ligo.org/bruce.edelman/gwinferno}) that implements the models 
described in this paper and performs hierarchical Bayesian inference with \textsc{NumPyro} and \textsc{Jax} \citep{pyro,numpyro,jax}. 
Our study paved the way as the first completely non-parametric compact object population study, employing data driven models for each of the hierarchically 
modeled population distributions. A complete understanding of the population properties of compact objects will help to advance poorly understood areas of stellar and 
nuclear astrophysics and provide a novel independent cosmological probe. With the coming influx of new data with the LVK's next observing run and the wide 
range of research avenues the compact object population will help to uncover, development of model-agnostic methods, such as the one we proposed here, will become necessary to efficiently make
sense of the data.

>>>>

Non-parametric and data-driven statistical modeling methods have been put to use with great success across the ever-growing field of gravitational 
waves \citep{B_Farr_etal_2014,Littenberg_2015,Mandel_2016,Edwards_2018,Doctor_GPR,Edelman_2021,Vitale_2021,Tiwari_2021_a,Tiwari_2021_b,Edelman_2022ApJ,Tiwari_2022ApJ}. 
We presented a case study exploring how basis splines make for an especially powerful and efficient data driven method of characterizing the binary black hole population observed 
with gravitational waves, along with the associated open source software \textsc{GWInferno} (\href[git.ligo.org/bruce.edelman/gwinferno]{https://git.ligo.org/bruce.edelman/gwinferno}) that implements the models 
described in this paper and performs hierarchical Bayesian inference with \textsc{NumPyro} and \textsc{Jax} \citep{pyro,numpyro,jax}. 
Our study paved the way as the first completely non-parametric compact object population study, employing data driven models for each of the hierarchically 
modeled population distributions. A complete understanding of the population properties of compact objects will help to advance poorly understood areas of stellar and 
nuclear astrophysics and provide a novel independent cosmological probe. With the coming influx of new data with the LVK's next observing run and the wide 
range of research avenues the compact object population will help to uncover, development of model-agnostic methods, such as the one we proposed here, will become necessary to efficiently make
sense of the data.
